%-------------------------
% Resume in Latex
% Based on Jake's Resume Template
% Modified: dark blue section headings, light blue sub-headings,
% real embedded Font Awesome icons (requires XeLaTeX or LuaLaTeX)
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{geometry}

% ---- Margin and Layout Config ----
\geometry{
  letterpaper,
  left=0.4in,
  right=0.4in,
  top=0.4in,
  bottom=0.4in
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlist{topsep=0pt, itemsep=2pt, parsep=0pt}

% ---- Real Font Awesome icons (needs XeLaTeX or LuaLaTeX to compile) ----
% Font files ship alongside this .tex file in a "fonts" subfolder.
\newfontfamily\FABrands{fa-brands-400.ttf}[Path = ./fonts/]
\newfontfamily\FASolid{fa-solid-900.ttf}[Path = ./fonts/]

\newcommand{\faPhone}{{\FASolid\symbol{"F095}}}
\newcommand{\faEnvelope}{{\FASolid\symbol{"F0E0}}}
\newcommand{\faGlobe}{{\FASolid\symbol{"F0AC}}}
\newcommand{\faGithub}{{\FABrands\symbol{"F09B}}}
\newcommand{\faLinkedin}{{\FABrands\symbol{"F08C}}}

% Colors: dark blue for section headings, light blue for sub-headings
\definecolor{darkblue}{RGB}{0,51,102}
\definecolor{lightblue}{RGB}{70,130,180}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large\bfseries\color{darkblue}
}{}{0em}{}[\color{darkblue}\titlerule \vspace{-4pt}]

\titlespacing{\section}{0pt}{4pt}{2pt}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\color{darkblue}#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\huge \scshape Karnayana Rohith} \\ \vspace{2pt}
    \small Visakhapatnam, Andhra Pradesh, India \\ \vspace{2pt}
    \small
    \faPhone\ +91 97011 28085 \ $|$ \
    \faEnvelope\ \href{mailto:karnayanarohith@gmail.com}{karnayanarohith@gmail.com} \ $|$ \
    \faLinkedin\ \href{https://linkedin.com/in/rohith-karnayana}{linkedin.com/in/rohith-karnayana} \ $|$ \
    \faGithub\ \href{https://github.com/karnayanarohith}{github.com/karnayanarohith} \ $|$ \
    \faGlobe\ \href{https://rohithkarnayana.vercel.app}{rohithkarnayana.vercel.app}
\end{center}

%-----------PROFILE-----------
\section{Profile}
\small{Final-year B.Tech ECE student specializing in low-level systems security and agentic AI. Experienced in firmware exploitation, kernel debugging, and orchestrating multi-agent LLM systems. Targeting SOC L1 / Cybersecurity Analyst roles to apply hands-on skills in threat mitigation, log analysis, and secure system design.}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Andhra University College of Engineering}{Visakhapatnam, Andhra Pradesh}
      {Bachelor of Technology (B.Tech) in Electronics \& Communication Engineering | CGPA: 8.4/10}{2023 -- 2027}
    \resumeSubheading
      {Sri Gayathri Junior College}{Gotlam, Vizianagaram, Andhra Pradesh}
      {Intermediate (MPC) | Percentage: 95\%}{2021 -- 2023}
    \resumeSubheading
      {ZPHS Siripuram}{Siripuram, Srikakulam, Andhra Pradesh}
      {Secondary School Certificate (SSC) | Percentage: 85\%}{2021}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
     \item \textbf{\color{darkblue}Languages}{: C, Python, Bash, Assembly, JavaScript, SQL (PostgreSQL)}
     \item \textbf{\color{darkblue}Cybersecurity}{: CVE Research \& Exploitation, Log Analysis \& Forensics, MITRE ATT\&CK, Threat Triage \& Incident Response, IAM}
     \item \textbf{\color{darkblue}AI / ML}{: LangGraph (Agentic AI), Ollama (Local LLMs), Vector DBs (ChromaDB), FastAPI, PyTorch, OpenCV}
     \item \textbf{\color{darkblue}Systems \& OS}{: Embedded Linux, Android Bootloader Internals, process/memory debugging, filesystem structures}
     \item \textbf{\color{darkblue}Tools \& Utilities}{: Git, Docker, Linux CLI, GDB, ADB, Fastboot, Wireshark, Splunk, Wazuh}
    }
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{\color{darkblue}Aegis} $|$ \emph{Python, LangGraph, Ollama, ChromaDB, Docker} \ \faGithub\ \href{https://github.com/karnayanarohith/Aegis}{\underline{karnayanarohith/Aegis}} \ \textit{(in active development)}}{}
          \resumeItemListStart
            \resumeItem{Engineering an autonomous, dual-mode Blue/Red Team security agent orchestrated with LangGraph and local LLMs via Ollama.}
            \resumeItem{Building a RAG-based memory pipeline using ChromaDB to store and recall threat intelligence, vulnerability logs, and attack patterns.}
            \resumeItem{Containerizing modular tools for automated network reconnaissance, log analysis, and incident triage mapped to the MITRE ATT\&CK framework.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{\color{darkblue}EXT4 Forensic Recovery Tool} $|$ \emph{C, Linux, Systems Programming} \ \faGithub\ \href{https://github.com/karnayanarohith/Aegis_File_Recovery_Tool}{\underline{karnayanarohith/Aegis\_File\_Recovery\_Tool}}}{}
          \resumeItemListStart
            \resumeItem{Developed a low-level forensic recovery tool in C that parses raw EXT4 disk partitions directly without mounting the filesystem, recovering 13+ file types (including .pth, .h5, .pdf, and image formats) with 100\% recovery accuracy in testing.}
            \resumeItem{Programmed manual superblock, inode table, and directory entry parsers to locate and reconstruct unlinked data block chains.}
            \resumeItem{Designed an ncurses-based TUI with a read-only preview engine to ensure forensically sound, non-destructive file recovery operations.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart

      \resumeSubheading
        {Android Security \& Systems Research}{May 2026 -- July 2026}
        {Self-Directed Research, Realme C15 (MT6765)}{}
        \resumeItemListStart
          \resumeItem{\textbf{CVE \& Vulnerability Profiling:} Conducted MediaTek BROM exploit research to bypass Download Agent authentication using MTKClient and dump the device's seccfg partition. Mapped vulnerability attack surfaces on EOL firmware, profiling CVE-2022-20421 (Binder UAF) and CVE-2024-20106 (Type Confusion) via GDB and dmesg.}
          \resumeItem{\textbf{Custom ROM \& Recovery Deployment:} Executed bootloader unlocking via BROM RAM patching and resolved Android dynamic partition allocation errors during custom recovery flashing. Deployed LineageOS and set up a Kali NetHunter chroot environment to convert the device into a mobile penetration testing platform.}
        \resumeItemListEnd

      \resumeSubheading
        {Network Operations Lead}{March 2026}
        {ELEXCENTRA Hackathon, Andhra University College of Engineering}{}
        \resumeItemListStart
          \resumeItem{Engineered and managed the network infrastructure for a live, 5-hour hackathon supporting 400+ concurrent devices across 6 rooms.}
          \resumeItem{Configured and deployed Wi-Fi and physical LAN cabling using TP-Link switches along with D-Link and Netgear routers.}
          \resumeItem{Diagnosed and resolved real-time network congestion, signal degradation, and routing conflicts under pressure to ensure zero downtime.}
        \resumeItemListEnd

      \resumeSubheading
        {Machine Learning Research Assistant}{2025}
        {NEXUS Research Project, Andhra University (under Dr. Karri Chiranjeevi)}{}
        \resumeItemListStart
          \resumeItem{Engineered a real-time small object detection pipeline for industrial seals and tags utilizing PyTorch, CUDA, and the MMDetection framework.}
          \resumeItem{Benchmarked advanced CNN and Vision Transformer architectures including TOOD, Deformable DETR, and DINO.}
          \resumeItem{Achieved 98\% accuracy on large objects and improved small-object mAP from 0.0 to 0.28 via resolution scaling and custom data balancing.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements \& Honors}
    \begin{itemize}[leftmargin=0.15in, label={}]
      \small{
        \item \textbf{\color{darkblue}1st Place Champion, HackAP (2025)}: Co-engineered 'Foundra' (\faGithub\ \href{https://github.com/karnayanarohith/Foundra}{\underline{github.com/karnayanarohith/Foundra}}), an AI startup advisor orchestrating 11 autonomous LLM agents across 6 business development phases.
        \vspace{2pt}
        \item \textbf{\color{darkblue}Security Solver} (picoCTF, TryHackMe, OverTheWire): 20+ rooms completed, Bronze league (Top 5\%). Actively practicing hands-on exploitation and offensive security. Solving 'THE GAUNTLET' (\faGithub\ \href{https://github.com/karnayanarohith/THE-GAUNTLET}{\underline{github.com/karnayanarohith/THE-GAUNTLET}}) --- a 21-challenge security lab with public write-ups.
        \vspace{2pt}
        \item \textbf{\color{darkblue}Project Finalist, Smart India Hackathon \& AURORA 2.0 (2024)}: Developed computer vision models to analyze satellite imagery for illegal mining detection.
      }
    \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications \& Credentials}
    \begin{itemize}[leftmargin=0.15in, label={}]
      \small{
        \item \textbf{\color{darkblue}Centri Security} --- Blue Team Junior Analyst (BTJA)
        \item \textbf{\color{darkblue}Anthropic} --- Model Context Protocol (MCP) Developer
        \item \textbf{\color{darkblue}Kaggle} --- Machine Learning Certification
        \item \textbf{\color{darkblue}Cisco} --- Ethical Hacker path (18+ credentials), including: Application Vulnerability Exploitation; Post-Exploitation Techniques; Wireless Security
        \item \textbf{\color{darkblue}Deloitte} --- Cybersecurity Job Simulation (Log Analysis \& Incident Response)
        \item \textbf{\color{darkblue}Tata Group} --- Identity \& Access Management (IAM) Simulation
      }
    \end{itemize}

%-----------LANGUAGES-----------
\section{Languages}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item English (Professional), Telugu (Native)}
\end{itemize}

\end{document}
